Dynamic Transition Analysis with TIMES

### 2018-01-12 doc/poster.tex
title shouldn't include the initiative name
Former-commit-id: 035b4e0ce9e5e4dee0c04e5a5c9c6abccbd99ef1

\title{Dynamic Transition Analysis with TIMES\\ 
I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions} % Poster title

\author{\textbf{\textsc{Energy Analysis Division}}\\
        Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}}
\institute{University of Illinios at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, IL 61801}
%----------------------------------------------------------------------------------------

@@

\item Dynamic simulation of Japan's energy system in TIMES model generator using a heterogeneous model and realistic constraints will help develop near-term decarbonization strategies.
\item Policymakers will benefit from identification of high impact technologies, and creation of R\&D investment and infrastructure development timelines.
\item Simulations will quantify system sensitivity to technology readiness.

>>>>

\title{Dynamic Transition Analysis with TIMES}

\author{\textbf{Energy Analysis Division}\\
        \textbf{I\textsuperscript{2}CNER Initiative on Challenges in Energy 
        Assessment and Energy Transitions}\\
        Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}}
\institute{University of Illinios at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, IL 61801}
%----------------------------------------------------------------------------------------

@@

\item Dynamic simulation of Japan's energy system transition in the TIMES model 
        generator will help develop near-term decarbonization strategies.
\item Policymakers will benefit from identification of high impact technologies, and creation of R\&D investment and infrastructure development timelines.
\item Simulations will quantify system sensitivity to technology readiness.
